---
title: 'Exercise #2'
author: "Theresa Walter"
date: "12.01.2022"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# more internal settings can go here
# Consider help pages like:
# https://rmarkdown.rstudio.com/lesson-1.html
# https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf

```

### Loaded packages

```{r libraries, message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)
library(zoo)
```



## 1. Quality control procedures (4 QCPs)
Data set from HOBO 1076071 from 2021-12-13 00:00:00 until 2021-01-09 23:50:00

```{r echo=TRUE}
data <- read_csv('https://raw.githubusercontent.com/data-hydenv/data/master/hobo/2022/10_minute/10760710.csv',
		 show_col_types = FALSE)

data
```

### 1.1 Measurement range (Plausible values)
The measurement range of HOBO is for temperature from -20°C to 70°C in air.
```{r qcp1, echo=TRUE}
data <- data %>% 
	mutate(qcp1 = case_when(temp < -20 ~ 1, # flagging values < -20°C
		  temp > 70 ~ 1, # flagging values > 70°C
		  TRUE ~ 0))

data
```

Counting values with and without a flag for quality check 1:
```{r wrong values, echo=TRUE}
data %>% group_by(qcp1) %>% # groub by flag and no flag
	summarise(n = n()) %>%  # count values with and without flag
	ungroup()
```

**Question**: How many data points are outside the measurement range?

**Answer**: There are 4032 values inside the measurement range and 0 unplausible values.

### 1.2 Plausible rate of change

Is there a difference of more than 1 K between two consecutive temperature values?
```{r qcp2, eval = TRUE}
data <- data %>% mutate(qcp2 = if_else(abs(temp - lag(temp)) > 1 , # Difference of temperature value and the previous temperature value
				       1, 0)) #flagging values with big difference to their previous value

data
```

Counting values with and without a flag for quality check 2:
```{r bigSteps}

data %>% group_by(qcp2) %>% # groub by flag and no flag
	summarise(n = n()) %>%  # count values with and without flag
	ungroup()
```

There are 7 inplausible temperature values:

```{r time_diff, eval=TRUE}
data %>% filter(qcp2 == 1)
```

**Question**: Describe shortly how many data points failed during this QCP and discuss whether there is a certain daytime pattern of failure or not?

**Answer**: As the shortened four-week-dataset is used for the analysis, a comparison of the first temperature value with its previous value was not possible (NA). Within the remaining dataset 7 values have been found, which had a difference to their previous value fo more than 1 K. Those values are distributed over the second and third week of the measurement and between 6 AM and 6 PM. Influences from the use of the balcony, where the HOBO was located, are possibly recognisable here.

### 1.3 Minimum variability (Persistence)

Didn't the temperature value chanche during one hour?
```{r qcp3, echo=TRUE}
data <- data %>% mutate(qcp3 = if_else(temp == lag(temp, n = 1) &
				       	temp == lag(temp, n = 2) &
				       	temp == lag(temp, n = 3) &
				       	temp == lag(temp, n = 4) &
				       	temp == lag(temp, n = 5),
				       1, 0))

data
```

Counting values with and without a flag for quality check 3:
```{r invalide Values, echo=TRUE}
data %>% 
	group_by(qcp3) %>% # groub by flag and no flag
	summarise(n = n()) %>%  # count values with and without flag
	ungroup()
```

There are 76 flagged values for quality check 3. Do they show a special pattern during a day?
```{r invalide_values_distribution, echo=TRUE}
data_unpersistant <- data %>% filter(qcp3 == 1) %>% 
	mutate(hour = format(dttm, format="%H"))

dis_hour <- data_unpersistant %>% 
	group_by(hour) %>% # groub by hour
	summarise(n = n()) %>%  # count values 
	ungroup()
ggplot(dis_hour, aes(hour, n))+
	geom_col()
```

**Task**: Code in this section should analyses the persistance.
If temperature has not changed during the last 60 minutes (i.e. data point Ti plus 5 data points before from Ti−1 to Ti−5) the corresponding data point Ti failed in this QCP.

**Answer**: The dataset contains 76 values, which have the same tamperature value as their 5 previous values and therefore failed the quality check 3. Those values show no specific pattern over one day.

### 1.4 Light intensity

Are temperature values influenced by intense sunlight?
```{r qcp4}
data <- data %>% 
	mutate(sic = case_when(lux < 20000 ~ "cat1",
				       between(lux, 20000, 50000) ~ "cat2",
				       lux > 50000 ~ "cat3",
				       TRUE ~ "other")) %>%  # classify by Sky Illuminance Classes (cat 3 = intense sunlight, cat 2 = sunlight, cat 1 = no influence)
	mutate(qcp4 = case_when(
				(hour(dttm) < 6 & hour(dttm) >= 18) ~ 0, #set all qcp4 values for nighttime to 0
                           lag(sic, n = 3) == "cat3" ~ 1, #set 1 if cat3 +- 3 before or ahead
                           lag(sic, n = 2) == "cat3" ~ 1,
                           lag(sic) == "cat3" ~ 1,
                           sic == "cat2" ~ 1,
                           lead(sic) == "cat3" ~ 1,
                           lead(sic, n = 2) == "cat3" ~ 1,
                           lead(sic, n = 3) == "cat3" ~ 1,
                           
                           lag(sic) == "cat2" ~ 1, #set 0 if cat 2 +- 1 before or ahead
                           sic == "cat2" ~ 1,
                           lead(sic) == "cat2" ~ 1,
                           
                           TRUE ~ 0))

data
```
Counting values with and without a flag for quality check 4:
```{r invalide Values2, echo=TRUE}
data %>% 
	group_by(sic) %>% # groub by categories
	summarise(n = n()) %>%  # count values with and without flag
	ungroup()
```

**Task**: Discuss shortly how often and when during daytime the QCP4 flags bad data. Elaborate on some reasons for your results.

**Answer**: The HOBO was attached to an interior balcony on the north side of the building. Therefore, it is plausible that no values were measured during direct sunlight.

## 2. Synthesis

```{r synthesis, eval=TRUE}
synth <- data.frame(qcp = c("qcp1", "qcp2", "qcp3", "qcp4"),
		    flags = c(sum(data$qcp1, na.rm = TRUE),
		    	  sum(data$qcp2, na.rm = TRUE),
		    	  sum(data$qcp3, na.rm = TRUE),
		    	  sum(data$qcp4, na.rm = TRUE)))
ggplot(synth, aes(qcp, flags))+
	geom_col()
```
```{r synthTable, echo=FALSE}
synth
```
**Task**: Present a table or graph to show how many data points fail during the four specific QCPs. Discuss shortly the reasons for failure and compare the different QCPs against each other.

**Answer**: As shown in the graph above, the most fails were detected during quality check 3. There were found 76 temperature values, which were same as their 5 previous values. In quality check 2 only 7 temperature values were detected, which differ more than 1 K from their previous value.
No bad values were found in quality check 1 and 4.
Fails in quality check 2 (strong change in temperature) might happended because of human influence by using the balkony.
Fails in quality ckeck 3 are eventually caused by the slow reaction of temperature caused by the location of the HOBO at a inverted balcony where hardly any influence from wind etc. happens.

## 3. Results

### 3.1 Result (Flagging system: 10-minutes-values)

```{r res1, message=FALSE, warning=FALSE}
# combine all important data with information about measurement and results from quality check
qc_df <- data.frame(id = data$id, dttm = data$dttm, temp = data$temp, lux = data$lux, qcp1 = data$qcp1, qcp2 = data$qcp2, qcp3 = data$qcp3, qcp4 = data$qcp4) 

# summarize the qualiy cck resutls to one final flagging (flag_num)
qc_df <- qc_df %>%
mutate(qc_tot = qcp1 + qcp2 + qcp3) %>%
mutate(flag_num = if_else(qc_tot > 0, 1, 0)) %>%
mutate(flag_txt = if_else(qc_tot > 1, "bad", "good")) %>% 
	as_tibble()

qc_df
```

**Task**: At the end of the code section above you should generate one! tibble or data.frame named `qc_df` with all time information, all data points (temperature and lux) and your outcomes of the different QCPs.

### 3.2 Result (Aggregate to hourly series)

```{r res2, echo=TRUE, message=FALSE, warning=FALSE}
hobo_hourly_dummy <- qc_df %>%
	mutate(hour = format(dttm, format="%Y-%m-%d %H")) %>% 
	mutate(hour = cut(dttm, breaks = "hour")) %>%
	group_by(hour) %>%
	summarise_at(vars(temp, flag_num), ~ mean(.,na.rm = TRUE)) %>%
	mutate(temp_2 = if_else(flag_num < 0.3, temp, NULL)) 

hobo_hourly <- data.frame(dttm = hobo_hourly_dummy$hour, temp = round(hobo_hourly_dummy$temp_2, 4)) %>% 
	as_tibble()

write.csv(hobo_hourly, 'C:/Users/Theresa/0-Studium/ALU/Semester 1/Modul 4 Data Collection Storage Management/Timeseries_in_R/Timeseries_in_R-1/1_data_processed/meteo_stations/my_hobo.csv', row.names = FALSE)

hobo_hourly
```

**Task**: At the end of the code section above you should generate one! tibble or data.frame named `hobo_hourly` with averaged temperature values per hour or NA values (if the hour is flagged as bad data). See exercise description for more details.

-   First column: YYYY-DD-MM HH:MM:SS

-   Second column: Temperature values (4 digits), NA values possible
