---
title: "Modul 04 Exercise 3"
author: "Theresa Walter"
date: "14 1 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r packages}
library(tidyverse)
library(lubridate)
library(dplyr)
```

## Data Import

```{r dataimport, echo=FALSE}
dwd_airport <- read.csv('https://raw.githubusercontent.com/AserehtRetlaw/Timeseries_in_R-1/main/1_data_processed/meteo_stations/dwd_airport.csv')
dwd_airport$dttm <- ymd_hms(dwd_airport$dttm)

dwd_urban <- read.csv('https://raw.githubusercontent.com/AserehtRetlaw/Timeseries_in_R-1/main/1_data_processed/meteo_stations/dwd_urban.csv')
dwd_urban$dttm <- ymd_hms(dwd_urban$dttm)

uni_meteo <- read.csv('https://raw.githubusercontent.com/AserehtRetlaw/Timeseries_in_R-1/main/1_data_processed/meteo_stations/uni_meteo.csv')
uni_meteo$dttm <- ymd_hms(uni_meteo$dttm)

wbi <- read.csv('https://raw.githubusercontent.com/AserehtRetlaw/Timeseries_in_R-1/main/1_data_processed/meteo_stations/wbi.csv')
wbi$dttm <- ymd_hms(wbi$dttm)

my_hobo <- read.csv('https://raw.githubusercontent.com/AserehtRetlaw/Timeseries_in_R-1/main/1_data_processed/meteo_stations/my_hobo.csv')
my_hobo$dttm <- ymd_hms(my_hobo$dttm)
names(my_hobo)[names(my_hobo)=="temp"] <- "my_hobo"
```

## Combine time and temperature values

```{r }
refs <- full_join(my_hobo, dwd_airport, by = "dttm")
refs <- full_join(refs, dwd_urban, by = "dttm")
refs <- full_join(refs, uni_meteo, by = "dttm")
refs <- full_join(refs, wbi, by = "dttm")
```

## Compare by Graph

```{r compareByGraph}
refs_long <- refs %>%
	pivot_longer(cols = -c(dttm), # use all, but not 'dttm'
		     names_to = "station",
		     values_to = "temp")

ggplot(data = refs_long, aes(x = dttm, y = temp)) +
	geom_line(aes(colour = station)) +
	theme_minimal() +
	theme(legend.position = c(0.85,0.25))+
	labs(title = "Example plot: Comparison across stations",
	     subtitle = "13.12.2021 - 09.01.2022",
	     x = "Date", y = "Temperature (°C)")
```

## Regressions
```{r regressions}
hobo_airport <- lm(refs$my_hobo ~ refs$dwd_airport) #calculate regression between my HOBO and dwd airport Meteo Station

hobo_urban <- lm(refs$my_hobo ~ refs$dwd_urban) #calculate regression between my HOBO and dwd urban Meteo Station

hobo_uni <- lm(refs$my_hobo ~ refs$uni_meteo) #calculate regression between my HOBO and uni garden Meteo Station

hobo_wbi <- lm(refs$my_hobo ~ refs$wbi) #calculate regression between my HOBO and wbi Meteo Station

# Overview

overview_reg <- data.frame(dwd_airport = hobo_airport[[1]][1:2],
			   dwd_urban = hobo_urban[[1]][1:2],
			   uni = hobo_uni[[1]][1:2],
			   wbi = hobo_wbi[[1]][1:2])
overview_reg
```
*Result* dwd_urban shows the best regression with the measurements from my HOBO data. Uni Garden Meteo station shows a very similar regression and is closer from a local perspective, but at a way higher elevation than my HOBO. WBI is also localy close, but shows the third best regression.

For those reasons data from DWD urban station will be used for the fill-up-modeling.

```{r modeling}
a <- overview_reg$dwd_urban[1]
b <- overview_reg$dwd_urban[2]

refs <- refs %>% mutate(model = a + b * dwd_urban) %>% 
	mutate(th = if_else(is.na(my_hobo), model, my_hobo)) %>% # new column without NAs
	mutate(origin = if_else(is.na(my_hobo), "R", "H"))

refs	

```

## Hourly dataset

```{r hourlyDataset}
hourly_th <- tibble(dttm = refs$dttm, th = refs$th, origin = refs$origin)

hourly_th
```

## Export

```{r export}
write.csv(hourly_th, "C:/Users/Theresa/0-Studium/ALU/Semester 1/Modul 4 Data Collection Storage Management/Timeseries_in_R/Timeseries_in_R-1/1_data_processed/hourly/10760710_Th.csv", row.names = FALSE)

write.csv(overview_reg, "C:/Users/Theresa/0-Studium/ALU/Semester 1/Modul 4 Data Collection Storage Management/Timeseries_in_R/Timeseries_in_R-1/1_data_processed/hourly/regressions.csv", row.names = FALSE)

```